---
title: "Select"
subtitle: "select"
author: "really3Q"
institute: "Department of Econometrics and Business Statistics"
output:
  xaringan::moon_reader:
    lib_dir: libs
    yolo: FALSE
---

```{r setup, include=FALSE , echo = FALSE, message = FALSE, warning = FALSE}
options(htmltools.dir.version = FALSE)
```

```{r , echo = FALSE, message = FALSE, warning = FALSE}
library(readr)
library(tidyverse)
library(knitr)
library(plotly)
library(broom)
library(DT)
annual_number_of_deaths_by_cause <- read_csv("Data/annual-number-of-deaths-by-cause.csv", 
    col_types = cols(`Number of executions` = col_double()))
GDP <- read_csv("Data/GDP.csv")
```

```{r , echo = FALSE, message = FALSE, warning = FALSE}
df_global <-  annual_number_of_deaths_by_cause %>%
  filter(Year %in% c(1950:2018)) %>% 
  pivot_longer(
    cols =  -c(Country, Code, Year),
    names_to = "Death_cause",
    values_to = "Count"
  )

df_CI <- df_global %>%  
  filter(Country %in% c("China", "India"))

interest <- c(
  "Cardiovascular diseases",
  "Diabetes mellitus",
  "HIV/AIDS",
  "Neoplasms",
  "Nutritional deficiencies",
  "Malaria"
)
```



```{r , echo = FALSE, message = FALSE, warning = FALSE}
CI_Percent <- df_CI%>% 
  group_by(Country,
           Year) %>% 
  mutate(Total_death = sum(Count, na.rm = TRUE)*100
         ) %>% 
  group_by(Country,
           Year,
           Death_cause,
           Total_death) %>% 
  summarize(Percentage = Count/Total_death*100) %>% 
  group_by(Country,
           Death_cause) %>% 
  arrange(desc(Percentage)) %>% 
  filter(Death_cause %in% interest)

CI_Total <- df_CI %>%
  group_by(Country,
           Year,
           Death_cause) %>%
  mutate(Death_abs = sum(Count, na.rm = TRUE)) %>%
  filter(Death_cause %in% interest) %>%
  group_by(Year,
           Country,
           Death_cause,
           Death_abs) %>%
  summarise() %>%
  left_join(GDP, by = c ("Country" = "Entity", 
                         "Year" = "Year"))
```

```{r Percentage Change in China and India, echo = FALSE, message = FALSE, warning = FALSE}
Percentage_trend <- CI_Percent %>% 
  ggplot(aes(x = Year,
             y = Percentage,
             color = Death_cause))+
  geom_line() +
  theme_bw()+
  facet_wrap(~Country, nrow = 2, scales = "free_y")

Absolute_trend <- CI_Total %>% 
  ggplot(aes(x = Year))+
  geom_line(aes(y = Death_abs,
             color = Death_cause)) +
  geom_line(aes(y = gdppc*500)) +
  facet_wrap(~Country, nrow = 2, scales = "free_y") +
  theme_bw()
```

class: inverse 
## Interested Country: China and India
<br>
<br>
--
**Q1: What are the diseases that growing fastest in developing country?**
<br>
<br>
--
**Q2: How the diseases changes with the change of GDP per capita**
--

### 6 most typical diseases we focusing on 

#### Cardiovascular diseases

#### Diabetes mellitus
  
#### HIV/AIDS
  
#### Neoplasms
  
#### Nutritional deficiencies
  
#### Malari


---
## Percentage of the 6 Death causes in China and India
--

```{r percentage trend, echo = FALSE, message = FALSE, warning = FALSE, fig.align="center", out.width = '100%'}
ggplotly(Percentage_trend)
```

---

## Number of people that dead from the 6 deseases
--
```{r absolute trend, echo = FALSE, warning = FALSE, message = FALSE, fig.align="center", out.width = '100%'}
ggplotly(Absolute_trend)
```


---

## Number of death caused by "Cardiovascular diseases" and "Neoplasms" against GDP per capita
```{r Run regression with the number of deasease against GDP per capita, , echo = FALSE, warning = FALSE, message = FALSE}
CI_model <- CI_Total %>%
  filter(Death_cause %in% c("Cardiovascular diseases", "Neoplasms")) %>%
  group_by(Country,
           Death_cause) %>%
  nest() %>%
  mutate(model = map(
    .x = data,
    .f = function(x) {
      lm(Death_abs ~ gdppc,
         data = x)
    }
  ))

CI_coef <- CI_model %>%
  mutate (tidy = map(model, tidy)) %>%
  unnest(tidy) %>%
  select(Country, Death_cause, term, estimate) %>%
  pivot_wider(
    id_cols = c("Country", "Death_cause"),
    names_from = term,
    values_from = estimate
  ) %>%
  rename("Intercept" = "(Intercept)",
         "Slope" = "gdppc")

CI_model_fitness <- CI_model %>%
  mutate(glance = map(model, glance)) %>%
  unnest(glance) %>%
  select(Country, Death_cause, r.squared) %>%
  mutate(r.squared = round(r.squared, 2)) %>% 
  right_join(CI_coef) %>% 
  mutate(Intercept = round(Intercept, 2),
         Slope = round(Slope, 2))

datatable(CI_model_fitness)
```

#### For every 1 unit of gdppc increase, the number of death caused by the deceased will increase by the number of the slope.

#### R^2 means the percentage of variability observed in the target variable is explained by the regression model.








